---
title: "Creating R package -- first steps"
output:
  html_document:
    df_print: paged
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  # fig.path = "figures/README-",
  out.width = "100%"
)
```


## Managing package libraries

* Package structure and state. 
[4.7 Package libraries](https://r-pkgs.org/package-structure-state.html#library).

Here are the main two levers that control which libraries
are active, in order of scope and persistence:

1. Environment variables, like `R_LIBS` and `R_LIBS_USER`,
which are consulted at startup.
1. Calling `.libPaths()` with one or more filepaths.

```sh
mkdir -p ~/Library/R/4.0/library
```

```{sh}
cat ~/.Rprofile.site
```

```{sh}
echo $R_LIBS_USER
```

```{r}
.Library
.Library.site
```

In both cases we see two active libraries, consulted in this order:

1. A user library.
1. A system-level or global library.

```{r}
.libPaths()
```

```{r}
lapply(
  .libPaths(), 
  list.dirs, 
  recursive = FALSE, 
  full.names = FALSE)
```


## Check what is installed

```{r message=FALSE, warning=FALSE}
packageVersion("devtools")

options(buildtools.check = NULL)
# devtools::install_github("r-lib/devtools")
# packageVersion("devtools")
```

Optionally run:

```{r}
# tidyverse::tidyverse_update()
# tidyverse::tidyverse_conflicts()
tidyverse::tidyverse_packages()
```


## Create package

```{r}
library(devtools)
library(tidyverse)
library(fs)
```

```{r}
# ?fs::dir_info

# dir_info(all = TRUE) %>% 
#   select(path, type)
# dir_info(all = TRUE, regexp = "^[.]git$") %>% 
#   select(path, type)
dir_info(all = TRUE, regexp = "^[.]git$", invert = TRUE) %>% 
  select(path, type)
```

